Estimating Neighborhood Rents with Scraped Data

### 2018-06-05 manuscript/index.Rmd
catching a few typos in discussion

ggplot(bym_df %>% filter(model == "E. Spatial AR(1)"), 
         aes(x = listingQtr, y = value, group = GISJOIN, color = qtrDev, label = GISJOIN)) +
  geom_line(lwd = .25, color = "black", alpha = .5) +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  scale_color_viridis_c(option = "A", labels = scales::dollar) +
  xlab("") +
  ylab("Median 1B Rent\n") +
  labs(color="Quarterly\nDeviation") +
  theme_minimal() +
  theme(legend.key.width = unit(.1, "inch")) +
  ggsave(filename = "../output/bym_lineplot.png",
         width = 6, height = 3, dpi = 500)
```

@@

obs_map_series + bym_map_series +
  plot_layout(ncol = 1) +
  ggsave(filename = "../output/avp_map_series.png",
         width = 6, height = 5, dpi = 500)
```

@@

Finally, this paper has endeavored (perhaps a little too much...) to provide an example for using scraped rental housing listings for research, but also with to model for how Rmarkdown, Git and GitHub are transformative technologies for our disciplines. There are no free lunches with reproducibility: these open-source technologies demand that we learn how to incorporate them into our work. To the extent that this requires thinking about analysis beyond a userbase of 1, there can be some growing pains. However, there are some positive spillovers beyond improving the _science_ of social science---including new platforms and media for sharing research findings and ideas.

>>>>

ggplot(bym_df %>% filter(model == "E. Spatial AR(1)"), 
         aes(x = listingQtr, y = value, group = GISJOIN, color = qtrDev, label = GISJOIN)) +
  geom_line(lwd = .25, color = "black", alpha = .5) +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  scale_color_viridis_c(option = "A", labels = scales::dollar) +
  xlab("") +
  ylab("Median 1B Rent\n") +
  labs(color="Quarterly\nDeviation") +
  theme_minimal() +
  theme(legend.key.width = unit(.1, "inch")) +
  ggsave(filename = "../output/bym_lineplot.png",
         width = 6, height = 3, dpi =300)
```

@@

obs_map_series + bym_map_series +
  plot_layout(ncol = 1) +
  ggsave(filename = "../output/avp_map_series.png",
         width = 6, height = 5, dpi =300)
```

@@

Finally, this paper has endeavored (perhaps a little too much...) to provide an example of using scraped rental housing listings for research, but also to model how Rmarkdown, Git and GitHub are transformative  for our disciplines. There are no free lunches with reproducibility: these open-source technologies demand that we learn how to incorporate them into our work. To the extent that this requires thinking about analysis beyond a userbase of 1, there can be some growing pains. However, there are some positive spillovers beyond improving the _science_ of social science---including new platforms and media for sharing research findings.
